---
title: "NHS-R Recommended packages"
output: github_document
---

```{r setup, include=FALSE, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(tidyverse, tidylog, janitor, airtabler)

# a dataframe is impoted from the Airtable base using the airtabler package and the Airtable API
nhsrpack <- airtable(
    base = keyringr::decrypt_kc_pw('nhsrpackages'), 
    tables = c("packages")
  )

packages <- nhsrpack$packages$select() %>% 
  clean_names() 

```

Below you will find packages recommended by members of the NHS-R community. These have been grouped by the type of package and how it is typically applied in data analysis.  

In addition there are some links to useful scripts, websites and resources for other languages at the end of the document. 

## Data visualisation

```{r, include=TRUE, echo=FALSE,  results='asis', message=FALSE}

# This function repeats for each sub section of the readme.
# Packages data frame is split by category which is a field in the database
# packages are ordered alphabetically and then the data frame is split by each package
# using purr the variables within the data frames are accessed using '.$x' and printed using cat()
# each r chunk outputs markdown due to the chunk option results='asis'

invisible(packages %>% 
  filter(category=='Data visualisation') %>% 
  arrange(package_name) %>% 
  group_split(package_name) %>% 
    purrr::imap(.,~{
      cat("###", .$package_name, "\n")
      cat("\n")
      cat(.$package_function, "\n")
      cat("\n")
      cat( '[','GitHub url',']','(',.$git_hub,')', "\n", sep = '')
      cat("\n")
      cat("\n")
    })
  )

```


---

## Data wrangling

```{r, include=TRUE, echo=FALSE,  results='asis', message=FALSE}
invisible(packages %>% 
  filter(category=='Data wrangling') %>% 
  arrange(package_name) %>% 
  group_split(package_name) %>% 
    purrr::imap(.,~{
      cat("###", .$package_name, "\n")
      cat("\n")
      cat(.$package_function, "\n")
      cat("\n")
      cat( '[','GitHub url',']','(',.$git_hub,')', "\n", sep = '')
      cat("\n")
      cat("\n")
    })
  )
```


---

## Database

```{r, include=TRUE, echo=FALSE,  results='asis', message=FALSE}
invisible(packages %>% 
  filter(category=='Database') %>% 
  arrange(package_name) %>% 
  group_split(package_name) %>% 
    purrr::imap(.,~{
      cat("###", .$package_name, "\n")
      cat("\n")
      cat(.$package_function, "\n")
      cat("\n")
      cat( '[','GitHub url',']','(',.$git_hub,')', "\n", sep = '')
      cat("\n")
      cat("\n")
      cat("\n")
    })
  )
```


---

## Hospital Coding

```{r, include=TRUE, echo=FALSE,  results='asis', message=FALSE}
invisible(packages %>% 
  filter(category=='Hospital Coding') %>% 
  arrange(package_name) %>% 
  group_split(package_name) %>% 
    purrr::imap(.,~{
      cat("###", .$package_name, "\n")
      cat("\n")
      cat(.$package_function, "\n")
      cat("\n")
      cat( '[','GitHub url',']','(',.$git_hub,')', "\n", sep = '')
      cat("\n")
      cat("\n")
      cat("\n")
    })
  )
```


---

## Modelling

```{r, include=TRUE, echo=FALSE,  results='asis', message=FALSE}
invisible(packages %>% 
  filter(category=='Modelling') %>% 
  arrange(package_name) %>% 
  group_split(package_name) %>% 
    purrr::imap(.,~{
      cat("###", .$package_name, "\n")
      cat("\n")
      cat(.$package_function, "\n")
      cat("\n")
      cat( '[','GitHub url',']','(',.$git_hub,')', "\n", sep = '')
      cat("\n")
      cat("\n")
      cat("\n")
    })
  )
```


---

## Reproducibility

```{r, include=TRUE, echo=FALSE,  results='asis', message=FALSE}
invisible(packages %>% 
  filter(category=='Reproducibility') %>% 
  arrange(package_name) %>% 
  group_split(package_name) %>% 
    purrr::imap(.,~{
      cat("###", .$package_name, "\n")
      cat("\n")
      cat(.$package_function, "\n")
      cat("\n")
      cat( '[','GitHub url',']','(',.$git_hub,')', "\n", sep = '')
      cat("\n")
      cat("\n")
      cat("\n")
    })
  )
```


---

## External data resource

```{r, include=TRUE, echo=FALSE,  results='asis', message=FALSE}
invisible(packages %>% 
  filter(category=='External data resource') %>% 
  arrange(package_name) %>% 
  group_split(package_name) %>% 
    purrr::imap(.,~{
      cat("###", .$package_name, "\n")
      cat("\n")
      cat(.$package_function, "\n")
      cat("\n")
      cat( '[','GitHub url',']','(',.$git_hub,')', "\n", sep = '')
      cat("\n")
      cat("\n")
      cat("\n")
    })
  )
```


---

## R Development

```{r, include=TRUE, echo=FALSE,  results='asis', message=FALSE}
invisible(packages %>% 
  filter(category=='R Development') %>% 
  arrange(package_name) %>% 
  group_split(package_name) %>% 
    purrr::imap(.,~{
      cat("###", .$package_name, "\n")
      cat("\n")
      cat(.$package_function, "\n")
      cat("\n")
      cat( '[','GitHub url',']','(',.$git_hub,')', "\n", sep = '')
      cat("\n")
      cat("\n")
      cat("\n")
    })
  )
```


---

## Rstudio Plugin

```{r, include=TRUE, echo=FALSE,  results='asis', message=FALSE}
invisible(packages %>% 
  filter(category=='Rstudio Plugin') %>% 
  arrange(package_name) %>% 
  group_split(package_name) %>% 
    purrr::imap(.,~{
      cat("###", .$package_name, "\n")
      cat("\n")
      cat(.$package_function, "\n")
      cat("\n")
      cat( '[','GitHub url',']','(',.$git_hub,')', "\n", sep = '')
      cat("\n")
      cat("\n")
      cat("\n")
    })
  )
```


---

## Rscript or function

```{r, include=TRUE, echo=FALSE,  results='asis', message=FALSE}
invisible(packages %>% 
  filter(category=='Rscript or function') %>% 
  arrange(package_name) %>% 
  group_split(package_name) %>% 
    purrr::imap(.,~{
      cat("###", .$package_name, "\n")
      cat("\n")
      cat(.$package_function, "\n")
      cat("\n")
      cat( '[','GitHub url',']','(',.$git_hub,')', "\n", sep = '')
      cat("\n")
      cat("\n")
      cat("\n")
    })
  )
```


---

## Links

```{r, include=TRUE, echo=FALSE,  results='asis', message=FALSE}
invisible(packages %>% 
  filter(category=='Link') %>% 
  arrange(package_name) %>% 
  group_split(package_name) %>% 
    purrr::imap(.,~{
      cat("###", .$package_name, "\n")
      cat("\n")
      cat(.$package_function, "\n")
      cat("\n")
      cat( '[','GitHub url',']','(',.$git_hub,')', "\n", sep = '')
      cat("\n")
      cat("\n")
      cat("\n")
    })
  )
```

---

## Resources in other languages

```{r, include=TRUE, echo=FALSE,  results='asis', message=FALSE}
invisible(packages %>% 
  filter(category=='Resources in other languages') %>% 
  arrange(package_name) %>% 
  group_split(package_name) %>% 
    purrr::imap(.,~{
      cat("###", .$package_name, "\n")
      cat("\n")
      cat(.$package_function, "\n")
      cat("\n")
      cat( '[','GitHub url',']','(',.$git_hub,')', "\n", sep = '')
      cat("\n")
      cat("\n")
      cat("\n")
    })
  )
```
